Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-19 WRITEUP/ms.tex
proof-read

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. Right: contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

@@

% Check with Shane
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF). In each model, we employ
$\sim$50,000 samples as the initial ``burn-in'' stage to stabilize the Markov
chains (which we then discard). We use the final $\sim$5,000
samplings to determine the posterior probability distributions. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.

@@

Our model parameters in \Tab{lens}, describing
the mass distribution of the lensing galaxy, are consistent (within the uncertainties)
with that of the SIE model presented by C06. We find a mass of
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
within the Einstein radius.
\input{table_medianLens}
\input{table_magFactor}

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is non-negligible for the CO emission, where its red wing
is apparently much brighter than the blue wing, which is consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near/at the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO thus ranges from 8.7 to 3.1 (\Tab{model}).

>>>>

\begin{figure}[!htbp]
\centering
% [height=1in,width=5in]
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. Right: contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

@@

% Check with Shane
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF). In each model, we employ
$\sim$50,000 samples as the initial ``burn-in'' stage to stabilize the Markov
chains (which we then discard). We use the final $\sim$5,000
samplings to determine the posterior probability distributions. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

Our model parameters in \Tab{lens}, describing
the mass distribution of the lensing galaxy, are consistent (within the uncertainties)
with that of the SIE model presented by C06. We find a mass of
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
within the Einstein radius.

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the red wing
of \bco is apparently much brighter than that in the blue wing, consistent 
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).
